---
title: "Prepare bill labels from CRS and CBP"
author: 
  - "Cole Tanigawa-Lau"
date: ""
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float: yes
    theme: paper
editor_options:
  chunk_output_type: console
params: 
  from_raw: FALSE
  dev:   FALSE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 5)
proj_dir <- tryCatch(rprojroot::find_rstudio_root_file(),
                     error = function(e) rprojroot::find_root(".gitignore"))

knitr::opts_knit$set(root.dir = proj_dir)
```

```{r about, echo=FALSE, results = "asis"}
cat(
    sprintf("Updated: %s.", 
            format(Sys.time(), "%b %d, %Y at %H:%M:%S", usetz = TRUE)),
    sprintf("Working directory: `%s`.", getwd()),
    sep = "\n\n"
)
```

This document organizes the ProPublica data on congressional legislation. 

There are dev packages like `rsunlight` to query the ProPublica and OpenStates APIs. They aren't reliable and don't permit bulk downloads. It's easiest to bypass query limits and click-download from links.

Source: https://www.propublica.org/datastore/dataset/congressional-data-bulk-legislation-bills

Data documentation: https://github-wiki-see.page/m/unitedstates/congress/wiki/Bills


Reads:

  - ~Adams mapping from CRS codes to topics: data/topic_labels/label_codings.csv~
   
    - Adam didn't include the 24 more general topics
   
  - Congressional Bills Project codings: data/topic_labels/bills93-114.csv
  - Legislation: zip files in data/legislation/propublica
  - Legislator ID codes: data/congress_ids.csv
  - Bill text: data/legislation/govinfo/bill_text.parquet

Writes:

- Bill metadata + topics: data/legislation/propublica/bills_list.qs
- Bill-legislator sponsorship with FEC IDs: data/legislation/propublica/sponsorship.qs

# Setup

```{r packages, warning=FALSE, message=FALSE}
tictoc::tic()
rm(list = setdiff(ls(), "params"))

library(fst)
library(qs)
library(arrow)
library(stringr)
library(data.table)
library(jsonify)
library(jsonlite)
library(purrr)
library(furrr)
library(coler)
library(dplyr)
library(tidyr)
library(tidylog)

source("code/functions.R")

if(!exists("params")) params <- list(dev = interactive())
if(params$dev) plan(multisession) else plan(multicore)
```

```{r}
cbp_bills <- fread("data/topic_labels/bills93-114.csv")

# Clicked links here from 1999-present:
# https://www.propublica.org/datastore/dataset/congressional-data-bulk-legislation-bills
# Then moved them to propublica subdir
pp_dir <- "data/legislation/propublica"
```

# Organize data

Unzip bulk data files.
```{r unzip, eval = params$from_raw}
# Find files not marked as unzipped
zips <- list.files(pp_dir, patt = "[0-9]\\.zip", full = TRUE, recursive = FALSE)
names(zips) <- gsub("\\.zip", "", zips)


map(names(zips), dir.create)

future_map(names(zips),
           function(nm) { 
               
               unzip(zips[[nm]], exdir = nm); 
               
               # Mark as unzipped
               zips[[nm]] %>% 
               { file.rename(., gsub(".zip", "unz.zip", x = ., fixed = TRUE)) }
           }
)
```

Read in the JSON files and store as R lists.
```{r qsave_jsons, eval = params$from_raw}
sessions <- 106:116
pp_read_dirs <- file.path(pp_dir, sessions)

pp_paths <-
    future_map(pp_read_dirs, list.files, 
               recursive = TRUE, full.names = TRUE,
               pattern = ".json") %>% 
    unlist()

qsave(pp_paths, "data/legislation/propublica/pp_paths.qs")
pp_paths <- qread("data/legislation/propublica/pp_paths.qs")

bills_jslist <- 
    future_map(pp_paths, from_json, simplify = TRUE, fill_na = TRUE)
qsave(bills_jslist, "data/legislation/propublica/pp_bills_jslist.qs")
```

Standardize bills and amendments data into an R object.

```{r json_to_bill, eval = params$from_raw}
bills_jslist <- 
    qread("data/legislation/propublica/pp_bills_jslist.qs")

bill_ids  <- map(bills_jslist, "bill_id")

system.time(bills <- map(bills_jslist, jslist_to_bill))
#     user   system  elapsed 
# 1145.487   25.995 1202.459 
names(bills) <- map(bills, "bill_id")

qsave(bills, "data/legislation/propublica/bills_list.qs")
```


# Link legislation to topics {.tabset}

```{r}
bills <- qread("data/legislation/propublica/bills_list.qs")
topics_list <- map(bills, "topics")
```

## Coarsened CRS lookup

I coded the top 250 CRS-assigned tags into broader topic labels. More details in localism project. Next I create a table linking to broader topics. Could expand if there are too many unlabeled bills after this grouping.
```{r}
subj_vec <- unlist(map(topics_list, "subjects"))

subj_tags <- 
    list(
    state_local = c("State and local government operations",
                    "Intergovernmental relations", 
                    "Federal-state relations", "State laws",
                    "State and local finance", "Federal preemption"),
    dc = "District of Columbia",
    california = "California",
    alaska = "Alaska",
    texas = "Texas",
    virginia = "Virginia",
    health  = c("Health", "Medicare", "Health care coverage and access",
                "Child health", "Health care costs and insurance",
                "Health programs administration and funding",
                "Health personnel", "Health promotion and preventive care",
                "Medicaid", "Emergency medical services and trauma care",
                "Health information and medical records",
                "Mental health", "Infectious and parasitic diseases",
                "Health facilities and institutions",
                "Cardiovascular and respiratory health",
                "Women's health", "Medical tests and diagnostic methods",
                "Disability and paralysis", 
                "Drug, alcohol, tobacco use", "Drug abuse",
                "Health insurance", "Hospital care", "Prescription drugs",
                "Access to health care", "Health care quality"),
    housing = c("Housing and community development"),
    human_serv = c("Social welfare", "Families", "Emergency management",
                   "Housing and community development", "Medicare",
                   "Department of Health and Human Services",
                   "Health programs administration and funding",
                   "Veterans' medical care",
                   "Health promotion and preventive care", "Medicaid",
                   "Disabled", "Water quality",
                   "Social work, volunteer service, charitable organizations",
                   "Immigration status and procedures",
                   "Veterans' education, employment, rehabilitation",
                   "Crime victims", "Child safety and welfare",
                   "Poverty and welfare assistance",
                   "Disaster relief and insurance",
                   "Department of Veterans Affairs",
                   "Indian social and development programs"),
    civil_rights = c("Civil rights and liberties, minority issues",
                     "Minorities", "Human rights", "Women",
                     "Racial and ethnic relations",
                     "Education of the disadvantaged"),
    foreign_natsec = c("Armed forces and national security",
                       "International affairs",
                       "Foreign trade and international finance",
                       "Terrorism", "Emergency management",
                       "Immigration", "Tariff", "Tariffs",
                       "Department of Homeland Security",
                       "Latin America", 
                       "Asia", "Europe",
                       "Diplomacy, foreign officials, Americans abroad",
                       "International organizations and cooperation",
                       "Foreign aid and international relief",
                       "Middle East",
                       "Immigration status and procedures",
                       "Department of Defense",
                       "Conflicts and wars", "Federal-Indian relations",
                       "Caribbean area", "Middle East and North Africa",
                       "United Nations", "Visas and passports",
                       "Trade restrictions", "Iraq",
                       "Border security and unlawful immigration",
                       "Military operations and strategy",
                       "Intelligence activities, surveillance, classified information", "Military medicine"),
    governance = c("Government operations and politics", "Congress", "Law",
                   "Government paperwork", 
                   "Executive agency funding and structure",
                   "Administrative remedies", "Executive reorganization",
                   "Elections, voting, political campaign regulation",
                   "Presidents and presidential powers, Vice Presidents"),
    legislative = c("Congress",
                    "House of Representatives",
                    "Legislative rules and procedure",
                    "Members of Congress",
                    "Legislation", "House rules and procedure",
                    "Senate"
                    ),
    funding = c("Government trust funds", "Appropriations",
                "Public contracts and procurement", "Authorization",
                "Grants-in-aid"),
    law = c("Law", "Administrative remedies", 
            "Civil actions and liability", 
            "Criminal investigation, prosecution, interrogation",
            "Right of privacy", "Actions and defenses",
            "Department of Justice", "Government liability"),
    oversight = c("Congressional oversight", 
                  "Government information and archives",
                  "Congressional reporting requirements",
                  "Government studies and investigations",
                  "Executive agency funding and structure",
                  "Administrative procedure", 
                  "Governmental investigations",
                  "Advisory bodies", "Performance measurement",
                  "Federal advisory bodies",
                  "Government ethics and transparency, public corruption",
                  "Congressional investigations"),
    regulation = c("Administrative law and regulatory procedures",
                   "Administrative procedure", 
                   "Licensing and registrations", "Licenses",
                   "Standards", "Nonprofit organizations",
                   "Elections, voting, political campaign regulation",
                   "Intellectual property", "Firearms and explosives",
                   "Accounting and auditing", 
                   "Banking and financial institutions regulation"),
    crime = c("Crime and law enforcement", 
              "Criminal investigation, prosecution, interrogation",
              "Fines (Penalties)", "Law enforcement officers",
              "Fraud offenses and financial crimes",
              "Law enforcement administration and funding",
              "Criminal justice information and records",
              "Crime victims", "Detention of persons",
              "Crime prevention", "Department of Justice",
              "Drug abuse", "Drug trafficking and controlled substances",
              "Criminal procedure and sentencing", "Violent crime",
              "Fraud", "Sex offenses"),
    educ   = c("Education", "Higher education", 
               "Elementary and secondary education",
               "Education programs funding", 
               "Student aid and college costs", "Federal aid to education",
               "Teaching, teachers, curricula", "Medical education",
               "Secondary education", "Education of the disadvantaged",
               "Health education"),
    transport = c("Transportation and public works",
                  "Infrastructure", "Transportation safety and security",
                  "Aviation and airports", 
                  "Transportation programs funding",
                  "Roads and highways", "Motor vehicles",
                  "Department of Transportation"),
    business = c("Commerce", "Small business", 
                 "Licensing and registrations",
                 "Business records", "Licenses",
                 "User charges and fees", "Consumer affairs",
                 "Tax deductions", "Business investment and capital",
                 "Public-private cooperation", "Consumer education",
                 "Tax exclusion", "Corporate finance and management",
                 "Consumer credit"),
    labor = c("Labor and employment", "Employment and training programs",
              "Wages and earnings", "Employee benefits and pensions",
              "Unemployment", 
              "Employment discrimination and employee rights",
              "Employee training"),
    agriculture = c("Agriculture and food"),
    finance     = c("Economics and public finance", 
                    "Finance and financial sector",
                    "Government lending and loan guarantees",
                    "Securities", "Department of the Treasury",
                    "Financial services and investments",
                    "Housing finance and home ownership",
                    "Inflation and prices"),
    tax = c("Taxation", "Income tax", "Tariff", "Tariffs",
            "Income tax credits", "Tax credits",
            "Tax administration and collection, taxpayers",
            "Income tax deductions", "Tax deductions", 
            "Income tax exclusion", "Budget deficits and national debt",
            "Tax exclusion", "Sales and excise taxes"),
    environment  = c("Public lands and natural resources",
                     "Environmental protection", "Land transfers",
                     "Water resources development",
                     "Marine and coastal resources, fisheries",
                     "Animals", "Water quality", "Oil and gas",
                     "Environmental assessment, monitoring, research",
                     "Alternative and renewable resources",
                     "Land use and conservation", 
                     "Hazardous wastes and toxic substances",
                     "Air quality", "Energy efficiency and conservation",
                     "Climate change and greenhouse gases",
                     "Water use and supply", "Department of the Interior",
                     "Wildlife conservation and habitat protection",
                     "Parks, recreation areas, trails",
                     "Outdoor recreation"),
    rural_urban = c("Rural conditions and development"),
    energy = c("Energy", "Oil and gas", 
               "Electric power generation and transmission"),
    science_tech = c("Science, technology, communications",
                     "Medical research", "Research and development",
                     "Research administration and funding",
                     "Internet and video services", "Data banks",
                     "Health technology, devices, supplies", "Internet",
                     "Computers and information technology",
                     "Computer security and identity theft",
                     "Electronic government information",
                     "Telephone and wireless communication"),
    fed_employ = c("Government employee pay, benefits, personnel management", 
                   "Military personnel and dependents",
                   "Federal employees", "Federal officials",
                   "Postal service", "Government contractors"),
    symbolic = c("Congressional tributes", "Commemorations",
                 "Commemorative events and holidays", "Names"),
    publicity = c("Government publicity"),
    society = c("Sports and recreation", "Arts, culture, religion", 
                "History"),
    religion = c("Religion")
    ) %>% stack() %>% 
  rename(subject = "values", tag = "ind")
```


```{r}
setDT(subj_tags, key = "subject")
subj_tags[ , tag := as.character(tag)]
```

## Label with broader topics
Group `bill_subjects` column into broader topic tags. Create columns flagging the presence of a topic in each bill. Using the `crs_topics` data.table isn't necessary since we'll need to output a JSON file of topics.
```{r}
# Create data.table of topic columns to fill
crs_topics <- data.table(bill_id = unique(names(bills)))

uniq_topics <- unique(subj_tags$tag)
for(topic in uniq_topics) set(crs_topics, j = topic, value = 0)

setkey(crs_topics, bill_id)
```


```{r subjects_to_topics}
crs_topic_list <- 
    map(topics_list,
        function(bill) {
            # Coarsen CRS subjects to topics
            cn_tags <- subj_tags[bill$subjects, na.omit(unique(tag))]
            
            # Locate bill in topics DF by ID and flag the topic
            crs_topics[bill$bill_id, 
                       (cn_tags) := map(.SD, ~ .x + 1L),
                       .SDcols = cn_tags
            ]
            
            # Return character vector of coarsened topics
            return(cn_tags)
        }
    )
```


Most bills concern a few broad topics!
```{r crs_report}
crs_topics[ , -1] %>% rowSums() %>% summary()
```


## CBP topics (1973--2017, hand coded)

Recode the Congressional Bills Project data to include major topic tags. These were hand-coded for the single most important topic. Codebook is in Excel format and does not report why there are legislator-specific variables for a bill-level data set.

```{r}
cbp_topics <- 
  select(cbp_bills,
         bill_id = BillID, senate = Chamber, congress = Cong,
         num_cospons = Cosponsr, major = Major, minor = Minor,
         private = Private,
         pass_house = PassH, pass_senate = PassS, veto = Veto,
         # passed and signed into law
         ps_law = PLaw, party_majority = Majority) %>% 
  
  left_join(AgendasProjectTopicCodes, 
            by = c(major = "code_major"))

table(cbp_topics$topic_major, useNA = "always") %>% 
  sort()
```

```{r}
cbp_topics[ , 
            bill_id_pp := 
              gsub(",3})-([A-Z]*)-(\\d*)", 
                   "\\2\\3-\\1",
                   bill_id) %>% tolower()
            ]

# check
# cbp_topics[sample(.N, 20), .(bill_id, bill_id_pp)]
# sample(bills %>% names(), 20)

cbp_topic_list <- as.list(cbp_topics$topic_major)
names(cbp_topic_list) <- cbp_topics$bill_id_pp
```

<!-- ## Build bill-topic data frame -->

<!-- Convert to a data.frame of bills with CBP topics. Dropping sponsorship data for now. -->
<!-- ```{r} -->
<!-- bill_topic_text <-  -->
<!--   map(bills, -->
<!--       ~ data.table(bill_id   = .x$topics$bill_id, -->
<!--                    topic_cbp = .x$topics$cbp_topic, -->
<!--                    topic_crs = .x$topics$primary_topic, -->
<!--                    summary   = .x$topics$summary) -->
<!--       ) %>%  -->
<!--   rbindlist() -->
<!-- ``` -->

# Export
```{r}
write_json(crs_topic_list, "data/topic_labels/crs_labels.json")
write_json(cbp_topic_list, "data/topic_labels/cbp_labels.json")
```


```{r}
tictoc::toc()
```

