---
title: "Prepare bill labels from CRS and CBP"
author: 
  - "Cole Tanigawa-Lau"
date: ""
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float: yes
    theme: paper
    highlight: tango
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 7, fig.height = 5)
proj_dir <- tryCatch(rprojroot::find_rstudio_root_file(),
                     error = function(e) rprojroot::find_root(".gitignore"))

knitr::opts_knit$set(root.dir = proj_dir)
```

```{r about, echo=FALSE, results = "asis"}
cat(
    sprintf("Updated: %s.", 
            format(Sys.time(), "%b %d, %Y at %H:%M:%S", usetz = TRUE)),
    sprintf("Working directory: `%s`.", getwd()),
    sep = "\n\n"
)
```

Reads:

  - data/topic_labels/crs_labels.json
  - data/topic_labels/cbp_labels.json

Writes:

 - data/legislation/splits/bills_train_crs.parquet
 - data/legislation/splits/bills_test_crs.parquet
 - data/legislation/splits/bills_train_cbp.parquet
 - data/legislation/splits/bills_test_cbp.parquet
 - data/legislation/splits/bills_unlabeled.parquet

# Setup

```{r packages, warning=FALSE, message=FALSE}
rm(list = setdiff(ls(), "params"))

library(arrow)
library(dplyr)
library(data.table)
```

Read data.
```{r}
bills <- 
  read_parquet("data/legislation/govinfo/bill_text.parquet") %>% 
  filter(text != "")
```

```{r}
crs_topics <- jsonlite::read_json("data/topic_labels/crs_labels.json")
cbp_topics <- jsonlite::read_json("data/topic_labels/cbp_labels.json")

stopifnot(all(sapply(cbp_topics, length) == 1))

# Drop NULL elements
cbp_topics <- unlist(cbp_topics)
crs_topics <- crs_topics[sapply(crs_topics, length) > 0]
```

Plenty of labeled bills not in the govinfo download. Must drop these before data.table join.
```{r}
cbp <- data.table(id = names(cbp_topics), label = cbp_topics) %>% 
  filter(id %in% bills$id)

crs <- data.table(id = names(crs_topics), label = crs_topics) %>% 
  filter(id %in% bills$id)
```


We have about twice as many labelled bills from CBP compared to CRS. Create two test and train splits, one for each set of labels.

```{r}
# Subset to sets of labeled bills by data.table join
setDT(bills, key = "id")

bills_cbp <- bills[cbp$id]
bills_crs <- bills[crs$id]

bills_unlab <- bills[!c(cbp$id, crs$id)]
```


# Random 50/50 split
```{r}
set.seed(575)
index_train_crs <- sample(1:nrow(bills_crs), nrow(bills_crs)/2)
index_train_cbp <- sample(1:nrow(bills_cbp), nrow(bills_cbp)/2)
```


# Export
Export without topic labels since CRS has multiple labels per bill, and parquet doesn't handle list-type columns.
```{r}
write_parquet(bills_crs[index_train_crs, ],
              "data/legislation/splits/bills_train_crs.parquet")
write_parquet(bills_crs[-index_train_crs, ],
              "data/legislation/splits/bills_test_crs.parquet")


write_parquet(bills_cbp[index_train_cbp, ],
              "data/legislation/splits/bills_train_cbp.parquet")
write_parquet(bills_cbp[-index_train_cbp, ],
              "data/legislation/splits/bills_test_cbp.parquet")


write_parquet(bills_unlab, "data/legislation/splits/bills_unlabeled.parquet")
```


